---
title: "STAA566_HW2"
author: "Manda Abhinay Reddy"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
--- 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


I have chosen data of daily historical stock price of GameStop from February 2002 (the year it was listed) to January 2021 from kaggle. Through this assignment I would like check how the volume of stocks varies variation in prices. I have used the plotly functionality with all the necessary formatting techniques like Rangeslider and subplot functionality to merge two plots. 



```{r}
library(plotly)
library(tidyverse)
```

```{r}

GME <- read.csv("GME_Stock.csv")
GME$year <- format(as.Date(GME$date, format="%Y-%m-%d"),"%Y")
GME <- GME %>%
  group_by(year)%>%
  arrange(date)
         
head(GME, n=20)

```

```{r}

GME_closing <- plot_ly(GME, 
                x= ~ date,
                y= ~ close_price,
                name = 'Closing price',
                type = 'scatter', 
                mode = 'lines'
                ) %>% layout(title = "GameStop stockprice data day wise",
         xaxis = list(title="date"),
         yaxis = list(title = "Closing price"))
GME_closing
```

```{r}

GME_vol <- plot_ly(GME, 
        x= ~ date,
        y= ~ volume,
        name = 'Volume',
        type = 'scatter', 
        mode = 'lines'
        ) %>% layout(title = "GameStop stockprice data day wise",
         xaxis = list(title="date"),
         yaxis = list(title = "Volume"))
GME_vol
```



```{r fig.height=8, fig.width = 10}
GME_new <- subplot(list(GME_closing,GME_vol),
                              nrows = 2, 
                              shareX = TRUE,
                              titleX = FALSE)  %>%
  rangeslider() %>%
  layout(hovermode = "x")

GME_new <- GME_new %>% layout(title = "GameStop stockprice data day wise",
         xaxis = list(title="Date"),
         yaxis = list(title = "Price Vs Volume "))

GME_new
```



